Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-07-05 paper/manuscript.Rmd
Short title even shorter
Updated data accesibility

<!-- **Short title:** Competition for pollination vs. facilitation -->

@@

<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. -->

>>>>

<!-- **Short title:** Competition/facilitation in pollination -->

@@

<!-- **Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance.. -->
